---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(CBRT)
library(data.table)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(plotly)
library(Rmisc)

searchCBRT(c("GDP","balance"))

showSeriesNames("bie_gsyihhy")

myCBRTKey <- "HAtzh5JZmg"

#Obtain Quarterly GDP Data. "GDP calculated with fixed prices" is chosen.

GDP_Ex_Fix_1998_TRY_Thousand <- getDataSeries("TP.UR.GG01.S")

#To Get Year Over Year GDP Growth Data

GDP_Ex_Fix_1998_TRY_Thousand[, GDP_Growth := 100*(TP.UR.GG01.S - shift(TP.UR.GG01.S, n = 4L))/shift(TP.UR.GG01.S, n = 4L)]

GDP_Ex_Fix_1998_TRY_Thousand[, TP.UR.GG01.S := NULL]

#Deleting Missing Values

GDP_Growth_1 <- na.omit(GDP_Ex_Fix_1998_TRY_Thousand)

#

showSeriesNames("bie_odana6")

#Obtain Current Account Data. Frequency is chosen as "6", which means "Quarterly".

CAD_Mil_USD <- getDataSeries("TP.ODANA6.Q01", freq = 6)

#To make Growth and CAD's time range identical, some rows are deleted from CAD data.

CAD_Mil_USD_1 <- CAD_Mil_USD[-c(1:196, 267:285),]

#Year variable is created. Its values will be in the form "Year-Qi".

aa <- paste0(rep(seq(1999,2016), each = 4, length = 70), rep("-"), rep(c("Q1","Q2","Q3","Q4")))

GDP_Growth_1[, Year := aa]

CAD_Mil_USD_1[, Year := aa]

#Deleting time variable which is unnecessary.

GDP_Growth_1[, time := NULL]

CAD_Mil_USD_1[, time := NULL]

#Changing the Current Account variable's name as "CAD".

names(CAD_Mil_USD_1)[names(CAD_Mil_USD_1) == "TP.ODANA6.Q01"] <- "CAD"

#Change the order of columns to make the "Year" column first.

setcolorder(CAD_Mil_USD_1, c("Year", "CAD"))

setcolorder(GDP_Growth_1, c("Year", "GDP_Growth"))

#To make Growth and CAD's numeric values close to each other, CAD values will be transformed to "Billion USD" from "Million USD".

CAD_Bil_USD <- CAD_Mil_USD_1[, CAD := CAD/1000]

#To put both CAD and Growth into the same plot, following data table is created.

DT1 <- GDP_Growth_1[CAD_Bil_USD, on = "Year"]

#Function of the theme which will be used on the plots.

theme_omer <- function() { 
  theme(plot.title = element_text(color = "#3182bd",size = 24, face = "bold"),
        plot.subtitle = element_text(color = "#2b8cbe", size = 16, face = "bold"),
        panel.grid.major.x = element_line(size = 0.2, colour = "#a6cee3", linetype = "solid"),
        panel.grid.minor.x = element_line(size = 0.1, colour = "#a6cee3"),
        panel.grid.major.y = element_line(size = 0.2, colour = "#a6cee3", linetype = "solid"),
        panel.grid.minor.y = element_line(size = 0.1, colour ="#a6cee3"),
        panel.background = element_rect(fill = "#f7f7f7"),
        axis.line = element_line(size = 1.4, colour = "#9ecae1"),
        axis.title = element_text(size = 15, colour = "gray26", face = "bold"),
        axis.text = element_text(size = 12, colour = "gray38",face = "bold"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5),
        axis.ticks.length.y = unit(0.4,"cm"),
        axis.ticks.length.x = unit(0.4,"cm"),
        axis.title.x = element_text(vjust = 1),
        axis.text.x = element_text(angle = 45),
        axis.title.y = element_text(vjust = 2),
        plot.caption = element_text(size = 10,color = "#636363"),
        legend.position = "right",
        legend.title = element_text(size = 12)
  )
}

#To prevent x axis text's from overlapping to each other, some x axis texts is deleted by creating the vector "b" and adding "scale_x_discrete(breaks = b)" to plots. Also, angle of the texts is changed above in the theme function.  

b <- paste0(rep(seq(1999,2016), each = 1, length = 18), rep("-"), rep("Q1"))

#Horizontal line "Y = 0" is placed in the plots to make the origin more visible. "group = 1" is used to prevent an error. "Colorblind safe" colors are used in the plots.

#Plot of CAD

g1 <- ggplot(data = CAD_Bil_USD, aes(y = CAD, x = Year, group = 1)) + 
  geom_line(size = 1.5, color = "#ef6548") + theme_omer() + scale_x_discrete(breaks = b) + 
  geom_hline(yintercept = 0, color ="#2171b5", size = 1) +
  labs(title = "Current Account",
       subtitle = "Turkey",
       x = "Year", y = "CAD(Billion USD)",
       caption = "Source: CBRT")

ggplotly(g1) %>%
  layout(annotations = 
           list(x = 1, y = -0.3, text = "Source: CBRT", 
                showarrow = F, xref = 'paper', yref = 'paper', 
                xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0,
                font = list(size = 12, color = "#636363")), 
         title = list(text = paste0('Current Account',
                                    '<br>',
                                    '<sup>',
                                    'Turkey',
                                    '</sup>'))) %>% 
  add_annotations(x = 0, y = -0.3, text = "Figure 1", 
                  showarrow = F, xref = 'paper', yref = 'paper', 
                  xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0, 
                  font = list(size = 15, color = "gray26", face = "bold"))

#Plot of GDP Growth

g2 <- ggplot(data = GDP_Growth_1, aes(y = GDP_Growth, x = Year, group = 1)) + 
  geom_line(size = 1.5, color = "#ef6548") + theme_omer() + scale_x_discrete(breaks = b) +
  geom_hline(yintercept = 0, color ="#2171b5", size = 1) +
  labs(title = "GDP Growth",
       subtitle = "Turkey",
       x = "Year", y = "Growth(%)",
       caption = "Source: CBRT")

ggplotly(g2) %>%
  layout(annotations = 
           list(x = 1, y = -0.3, text = "Source: CBRT", 
                showarrow = F, xref = 'paper', yref = 'paper', 
                xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0,
                font = list(size = 12, color = "#636363")), 
         title = list(text = paste0('GDP Growth',
                                    '<br>',
                                    '<sup>',
                                    'Turkey',
                                    '</sup>'))) %>% 
  add_annotations(x = 0, y = -0.3, text = "Figure 2", 
                  showarrow = F, xref = 'paper', yref = 'paper', 
                  xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0, 
                  font = list(size = 15, color = "gray26", face = "bold"))

#Plot of CAD & GDP Growth

g3 <- ggplot(data = DT1, aes(x = Year, group = 1)) + 
  geom_line(aes(y = GDP_Growth, color = "GDP Growth(%)"), size = 1.5) +
  geom_line(aes(y = CAD, color = "CAD(Billion Dollar)"), size = 1.5) + theme_omer() + 
  scale_x_discrete(breaks = b) + geom_hline(yintercept = 0, color ="#2171b5", size = 1) +
  guides(col = guide_legend("")) +
  labs(title = "GDP Growth & Current Account",
       subtitle = "Turkey",
       x = "Year", y = "Growth and CAD",
       caption = "Source: CBRT")

ggplotly(g3) %>%
  layout(legend = list(x = 0.01, y = 0.01, bgcolor = "#E2E2E2"), 
         annotations = list(x = 1, y = -0.3, text = "Source: CBRT", 
                            showarrow = F, xref = 'paper', yref = 'paper', 
                            xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0,
                            font = list(size = 12, color = "#636363")), 
         title = list(text = paste0('GDP Growth & Current Account',
                                    '<br>',
                                    '<sup>',
                                    'Turkey',
                                    '</sup>'))) %>% 
  add_annotations(x = 0, y = -0.3, text = "Figure 3", 
                  showarrow = F, xref = 'paper', yref = 'paper', 
                  xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0, 
                  font = list(size = 15, color = "gray26", face = "bold"))



p1 <- ggscatter(DT1, x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "1999-2016")

p2 <- ggscatter(DT1[c(13:40)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2002-2008")

p3 <- ggscatter(DT1[c(41:52)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2009-2011")

p4 <- ggscatter(DT1[c(53:70)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2012-2016")

p5 <- ggscatter(DT1[c(9:20)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2001-2003") +
  geom_smooth(formula = y ~ x, method = "lm", se = FALSE)


multiplot(p1, p2, p3, p4, p5, cols = 3)
```

# Relation Between Current Account Balance and GDP Growth {.tabset}

## Current Account Balance Data {.tabset}

<font size="3"> As can be seen from Figure 1 (below), between 1999 and 2003, the current account balance is close to 0, takes both positive and negative values, between 2 and -5. After 2003, the current account deficit occurs every year and it takes values between -5 and -20. So, it can be said that 2003 is a transition year. Most probably, the economic policy of Turkey has changed this year. Especially between 2002 and 2008, the current account deficit increased sharply. By the effect of the 2008 crisis, the deficit dropped and came close to 0. In 2010 and 2011, the deficit increased again really fast and reached its highest values. However, after the first half of 2011, the deficit has begun to fall.
</font>

```{r, out.width = "120%", echo = F}

#Plot of CAB

g1 <- ggplot(data = CAD_Bil_USD, aes(y = CAD, x = Year, group = 1)) + 
  geom_line(size = 1.5, color = "#ef6548") + theme_omer() + scale_x_discrete(breaks = b) + 
  geom_hline(yintercept = 0, color ="#2171b5", size = 1) +
  labs(title = "Current Account",
       subtitle = "Turkey",
       x = "Year", y = "CAD(Billion USD)",
       caption = "Source: CBRT")

ggplotly(g1) %>%
  layout(annotations = 
           list(x = 1, y = -0.3, text = "Source: CBRT", 
                showarrow = F, xref = 'paper', yref = 'paper', 
                xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0,
                font = list(size = 12, color = "#636363")), 
         title = list(text = paste0('Current Account',
                                    '<br>',
                                    '<sup>',
                                    'Turkey',
                                    '</sup>'))) %>% 
  add_annotations(x = 0, y = -0.3, text = "Figure 1", 
                  showarrow = F, xref = 'paper', yref = 'paper', 
                  xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0, 
                  font = list(size = 15, color = "gray26", face = "bold"))

```

## GDP Growth Data {.tabset}

<font size="3"> As can be seen from Figure 2, Turkey's growth is not stable. One reason is that Turkey's economy is fragile and takes huge hits during crises. While the growth rate in the third quarter of 2000 is 8.5%, it has dropped to -9.8% in the last quarter of 2001 due to the 2001 crisis. Similarly, in 2009, the growth rates have dropped to -14.7% due to the 2008 crisis. The growth rate reached 11% in 2002. Let's compare after 2001 and after 2008 crisis. After the 2001 crisis, growth rates take values between 3% and 12%. After the 2008 crisis, growth rates take values between 1% and 12%. However, after 2012, growth rates take values between 0% and 5%, which means growth is low at these years. To sum up, the worst years in terms of growth are 2012-2016 and the best years are 2002-2008. Growth rates in 2010 and 2011 are really high but it is a short period. </font>

```{r, out.width = "120%", echo = F}

#Plot of GDP Growth

g2 <- ggplot(data = GDP_Growth_1, aes(y = GDP_Growth, x = Year, group = 1)) + 
  geom_line(size = 1.5, color = "#ef6548") + theme_omer() + scale_x_discrete(breaks = b) +
  geom_hline(yintercept = 0, color ="#2171b5", size = 1) +
  labs(title = "GDP Growth",
       subtitle = "Turkey",
       x = "Year", y = "Growth(%)",
       caption = "Source: CBRT")

ggplotly(g2) %>%
  layout(annotations = 
           list(x = 1, y = -0.3, text = "Source: CBRT", 
                showarrow = F, xref = 'paper', yref = 'paper', 
                xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0,
                font = list(size = 12, color = "#636363")), 
         title = list(text = paste0('GDP Growth',
                                    '<br>',
                                    '<sup>',
                                    'Turkey',
                                    '</sup>'))) %>% 
  add_annotations(x = 0, y = -0.3, text = "Figure 2", 
                  showarrow = F, xref = 'paper', yref = 'paper', 
                  xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0, 
                  font = list(size = 15, color = "gray26", face = "bold"))

```

## Relation Between Growth and CAB {.tabset}

<font size="3"> As can be seen from Figure 3, the highest growth rates match with both high and low current account deficits. However, it can be seen that during both 2001 and 2008 crises, as growth reached negative values, current account deficits fell or current account surplus occurred. The reason can be the low amounts of imports at crisis periods. It is not strong evidence expressing the relation between CAB and Growth. It should be supported by analysis for longer time periods. For both CAB and growth, 2002-2008 and 2012-2016 periods are different from each other. So, these time periods will be analyzed separately, in addition to an analysis for the whole data. Correlations on these time periods and correlation during crises will be found. </font> 

```{r, out.width = "120%", echo = F}

#Plot of CAB & GDP Growth

g3 <- ggplot(data = DT1, aes(x = Year, group = 1)) + 
  geom_line(aes(y = GDP_Growth, color = "GDP Growth(%)"), size = 1.5) +
  geom_line(aes(y = CAD, color = "CAD(Billion Dollar)"), size = 1.5) + theme_omer() + 
  scale_x_discrete(breaks = b) + geom_hline(yintercept = 0, color ="#2171b5", size = 1) +
  guides(col = guide_legend("")) +
  labs(title = "GDP Growth & Current Account",
       subtitle = "Turkey",
       x = "Year", y = "Growth and CAD",
       caption = "Source: CBRT")

ggplotly(g3) %>%
  layout(legend = list(x = 0.01, y = 0.01, bgcolor = "#E2E2E2"), 
         annotations = list(x = 1, y = -0.3, text = "Source: CBRT", 
                            showarrow = F, xref = 'paper', yref = 'paper', 
                            xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0,
                            font = list(size = 12, color = "#636363")), 
         title = list(text = paste0('GDP Growth & Current Account',
                                    '<br>',
                                    '<sup>',
                                    'Turkey',
                                    '</sup>'))) %>% 
  add_annotations(x = 0, y = -0.3, text = "Figure 3", 
                  showarrow = F, xref = 'paper', yref = 'paper', 
                  xanchor = 'right', yanchor = 'auto', xshift = 0, yshift = 0, 
                  font = list(size = 15, color = "gray26", face = "bold"))


```

## Correlation Between Growth and CAB {.tabset}

<font size="3"> For 2002-2008 and 2012-2016 time periods, correlation values are really close to 0, which indicates no relationship between variables. For 1999-2016, the correlation is equal to -0.37, which means that there is a weak negative relation. For 2001-2003 and 2009-2011 (during crisis periods), correlation values are -0.57 and -0.7, respectively. It indicates a moderate relationship between Growth and CAB.

During crises, there is a moderate or strong relation but for other times, there is no relationship. For the whole data, there is a weak correlation. So, without crises, there is not any relationship between Growth and CAB, but crisis periods show a strong relationship between the two and push the correlation value up. So, the value indicates that this weak relationship is misleading and it is even weaker probably.  </font>

```{r, echo = F, warning = FALSE, message = FALSE, out.width = "120%"}

#Correlation Plots

p1 <- ggscatter(DT1, x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "1999-2016")

p2 <- ggscatter(DT1[c(13:40)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2002-2008")

p3 <- ggscatter(DT1[c(41:52)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2009-2011")

p4 <- ggscatter(DT1[c(53:70)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2012-2016")

p5 <- ggscatter(DT1[c(9:20)], x = "CAD", y = "GDP_Growth", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "CAD(Bil.USD)", ylab = "Growth(%)") + labs(title = "2001-2003") +
  geom_smooth(formula = y ~ x, method = "lm", se = FALSE)


multiplot(p1, p2, p3, p4, p5, cols = 3)

```
